Locally-Oriented Programming:\\ A Simple Programming Model for Stencil-Based Computations on Multi-Level Distributed Memory Architectures

### 2015-02-04 papers/LOPe/programming-model.tex
Replied to \todo comment from Matt.

LOPe is a domain specific language (DSL) implemented as a small extension
to standard Fortran 2008\todo{What version of Fortran does it extend?}.
Fortran was chosen as the base language for LOPe, although in
principle, the same techniques could be applied to language such as C
or C++ (in conjuction with some form of array extensions such as those
proposed by Intel).  Fortran was chosen because it already provides a
rich array-based syntax.  Readers who are unfamiliar with Fortran
syntax may wish to consult Appendix A, for a brief description of
Fortran notation.

>>>>

LOPe is a domain specific language (DSL) implemented as a small extension
to standard Fortran 2008\todo{What version of Fortran does it extend? Not sure what you mean as F2008 is explicitly mentioned?}.
Fortran was chosen as the base language for LOPe, although in
principle, the same techniques could be applied to language such as C
or C++ (in conjuction with some form of array extensions such as those
proposed by Intel).  Fortran was chosen because it already provides a
rich array-based syntax.  Readers who are unfamiliar with Fortran
syntax may wish to consult Appendix A, for a brief description of
Fortran notation.
